%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%   LaTeX File for Doctor (Master) Thesis of Tsinghua University
%   LaTeX + CJK     清华大学博士（硕士）论文模板
%   Based on Wang Tianshu's Template for XJTU
%   Version: 1.00
%   Last Update: 2003-09-12
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%   Copyright 2002-2003  by  Lei Wang (BaconChina)       (bcpub@sina.com)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%   LaTeX File for xi'an Jiao Tong University
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%   Copyright 2001  by  Wang Tianshu    (tswang@asia.com)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\renewcommand{\baselinestretch}{1.5}
\fontsize{12pt}{13pt}\selectfont

\chapter[ABSTRACT]{\textsf{\textbf{Abstract}}}
\markboth{英~文~摘~要}{英~文~摘~要}
\noindent 
Numerical simulations of flows with complex solid-fluid boundary are
of great importance in industrial areas such as
Oil\&Gas recovery, renewabel energy development, chemical process and environment 
engineering. Lattice Boltzmann method(LBM) is a powerful tool
for simulating of these complex flow phenomenon due to its easy processing of 
solid-fuid boudary and ability of modeling of multiphase/multicomponent flow.

From the compuatational standpoint, LBM is well suited for parallel implementation.
On the  emerging massively parallel graphics processing units(GPU) platform, LBM exhabits
an extrodinary  performance at a rather low cost.  
The combining of the GPU and LBM is promising technique to simulate complex flow in complex
geometries.

In this work, parallel LBM simulators were developed within the CUDA GPU programming framework.
Using the simulators, we carried out simulation of single phase flow and mulitcompnet-multiphase flow in porous media.
We also investigate performance optimization techniques to deal with the 
complex geometries and interacation of components. 
Performance evalution and detailed analysis are conducted for the optimization techniques.

\vspace{1em}
\noindent {\textbf{Key Words:}} \quad lattice Boltzmann method, graphics processing units,
high performance computing, multiphase flow, porous media
